\section{Executive Summary}
% Breif Intro
At a world leading university it may be considered suprising to find out that there is not a single place of information that students can go to to find out more about what industries have to offer them. Instead they must trawl through websites, looking in different places for events, placements and job oppourtunities.
The Department of Computing does have a website for students to upload a curriculum vitate, but it is not well known amongst students and once their CV is uploaded, they have no way of telling if it has been read.
Furtheremore, this site actually hinders students by providing the company an alphabetical list of these CVs, leaving the company to download each before they can find out any further information. How many companies get to the bottom of the list? We cannot be sure but we expect this number to be minimal.
% What is it
The Corporate Partnership Program version 2.0 aims to address these issues by becoming a central hub for students and companies to promote themselves to one another.

In short the CPPv2.0 will allow students to:

\begin{itemize}
  \item Advertise themselves with a student profile
  \item Browse upcoming events
  \item Receive targeted emails, which we hope will increase the rate of emails that are actually read (rather than considered as spam)
  \item Sign up to events
  \item Become aware of placements
\end{itemize}

Furthermore it will allow companies to

\begin{itemize}
  \item Advertise events and placements
  \item Browse students based upon year, interestes etc.
  \item Send targeted emails to students
\end{itemize}

% Hmm not sure I like this section but I think it's important to say it frees up Will and Serenas time!
Finally it is of significant benefit to Indistrial Liaison Officers of all departments as they will

\begin{itemize}
  \item No longer be the middle man for sending of emails
  \item Be aware of companies contacting students
  \item Be aware of which companies are receiving student interest
  \item Given an overview of statistics and trends in the CPP ecosystem
\end{itemize}

% Why would I want it
We believe that our product will be of great use to students and companies because...

% Why now
The Department of Computing offers excellent learning facilities for students and has a world wide reputation, we feel we must uphold this with our Indistrual oppourtunities for students....
The current Coroporate Partnership Program has had a lot of recent interest from other departments and it is crucial that we provide them with an up to date exciting system for their students to use.
