\documentclass{article}
\usepackage[margin=1in]{geometry}

\begin{document}

\title{Corporate Partnership Program version 2.0}
\author{Peter Hamilton, Jack Stevenson, Sarah Tattersall, Tom Wilding \& Tom Wilshere}
\date{\today}         % inserts today's date
\maketitle            % generates the title from the data above
\pagebreak

\section{Executive Summary}
% Breif Intro
At a world leading university it may be considered suprising to find out that there is not a single place of information that students can go to to find out more about what industries have to offer them. Instead they must trawl through websites, looking in different places for events, placements and job oppourtunities.
The Department of Computing does have a website for students to upload a curriculum vitate, but it is not well known amongst students and once their CV is uploaded, they have no way of telling if it has been read.
Furtheremore, this site actually hinders students by providing the company an alphabetical list of these CVs, leaving the company to download each before they can find out any further information. How many companies get to the bottom of the list? We cannot be sure but we expect this number to be minimal.
% What is it
The Corporate Partnership Program version 2.0 aims to address these issues by becoming a central hub for students and companies to promote themselves to one another.

In short the CPPv2.0 will allow students to:

\begin{itemize}
  \item Advertise themselves with a student profile
  \item Browse upcoming events
  \item Receive targeted emails, which we hope will increase the rate of emails that are actually read (rather than considered as spam)
  \item Sign up to events
  \item Become aware of placements
\end{itemize}

Furthermore it will allow companies to

\begin{itemize}
  \item Advertise events and placements
  \item Browse students based upon year, interestes etc.
  \item Send targeted emails to students
\end{itemize}

% Hmm not sure I like this section but I think it's important to say it frees up Will and Serenas time!
Finally it is of significant benefit to Indistrial Liaison Officers of all departments as they will

\begin{itemize}
  \item No longer be the middle man for sending of emails
  \item Be aware of companies contacting students
  \item Be aware of which companies are receiving student interest
  \item Given an overview of statistics and trends in the CPP ecosystem
\end{itemize}

% Why would I want it
We believe that our product will be of great use to students and companies because...

% Why now
The Department of Computing offers excellent learning facilities for students and has a world wide reputation, we feel we must uphold this with our Indistrual oppourtunities for students....
The current Coroporate Partnership Program has had a lot of recent interest from other departments and it is crucial that we provide them with an up to date exciting system for their students to use.




\pagebreak
\section{Introduction}
The Corporate Partnership Program was designed to `promote the relationship between the Department of Computing and organisations who wish to recruit our students whilst investing in academic sponsorship'.
%http://www.doc.ic.ac.uk/cpp/
Students use the system by registering their CV's along with some tick box interests and corporate partners can browse these in their own time in order to contact students regarding internships, placements, and graduate oppourtunities.
However the system is very out dated and only provides companies with an unfilterable list of students. For example if a web development company wishes to recruit summer interns who have experience with Ruby on Rails they must look at every single CV in turn to ascertain if a student has this skill, something which is time consuming, frustrating, and realistically is unlikely to happen.
From the students side of view once they have uploaded their CV they have no way of enchacing their chances that a relevant company will view their CV.

The current system has other flaws, for example once it's been set up there is no way for administrators to tell which corporate partners are using the system and how many students are being contacted. What goes on with the system is really a black hole to the Department of Computing Industrial Liaison Officers. 

Furthermore other departments have expressed an interest in this system and is not deemed up to date enough to pass on to another department.

This is where our product comes into play, we have designed a system where students are given their own profile to maintain which very quickly shows a company their skills and interests before they have to download a CV. Students can then add their CV, resume, and any other releavnt documents, information about themselves and list their skills and interests.
When searching for a student companies can filter students via their skills and interests in order to reduce the number of irrelevant students they have to view. By making a system that makes finding students easier, we believe that companies will feel more encouraged to use this, rather than waiting 
for students to apply to them.

Our system also addresses some additional needs of the department that are currently not catered for by the current:
Our supervisors, Will Knottenbelt and Serena Coultress spend a vast amount of time forwarding company emails regarding events and placements to students.
Students often don't read these emails because of the large number they receive daily, not just from the Corporate Partnership Program, to their inboxes. Often an exciting event can be lost amidst everything else. Students also often get frustrated with the number of irrelevant Corporate Partnership Program emails they receive too, for example if a company wishes to advertise a female only event everyone at current receives it.
Shockingly many students don't spend time reading Coroporate Partnership emails due to the high amount that they perceve as uninteresting to them.

We therefore have tied the requirement of more relevant emails and an easier way to find out about events and placements into our system. By allowing companies to advertise events and placements on our site and having students alerted of these when they log into the system we believe that it free's
up a students inbox and allows them to see events when they're looking and interested rather than at a busy time when this event might slip through
unnoticed.
Students are also allowed to express desires in emails they do not wish to receive, such as female only information, to help make the Coroporate Partnership Program a more personal experience. 


We decided to tie this functionaility into the product by allowing companies to advertise these directly on our site, cutting out the middle man.
Students often receive emails but never read them, our system provides a far more interactive way of viewing this information in a way that can be easily found by the student, which we hope will encourage event participation.

Finally a huge gripe by students from our department is they get emails that are not relevant to them. For example if a company offers a female only work shop, male students should be given the option to opt out of these emails in order to avoid being spammed. Our system addresses these in ways that you will find out during the report.


\section{Design \& Implementation}
\section{Evaluation}
\section{Conclusion \& Future Extensions}
\section{Project Management}

\end{document}

