\section{Executive Summary}

\subsection{Overview:}
CPP: Connect helps find, establish, and encourage the relationships between university students and companies. It gives students, companies, and departments exactly what they want: students get in touch with their dream companies, find out about fantastic events, and seal the deal for jobs and placements. Companies get to target the students that fit their exact requirements, meet them at publicised events, and ultimately offer them jobs or placements. The department benefits by offering a more professional experience, enticing more companies to join the scheme, as well as reducing unnecessary administration.

\subsection{Problems with the existing system:}
The current system provides no cohesion between opportunities, events and student information. In particular there is no way at all to search for students and students access to company information is limited. This prohibits the process of pairing student and companies. 
Students have no way to express their interests and skills, therefore companies can only be presented with a list of student's names and CVs, as such searching for students that match their criteria is laborious and time consuming.

Events and placements provided by companies are only advertised via bulk emails which overload students and require an ongoing administrative process. On top of this, administrators have no way of evaluating the use of the system and are burdened with many unnecessary tasks.    
As the programme continues to expand, the need to impress companies and streamline the process is becoming more eminent. A new system is called for that helps the programme reach its full potential.

\subsection{Our solution:}
Our solution is a website that allows students to signup and make their own profile, upload their CV, and instantly browse companies and their events and placements. Companies likewise, can signup on the site and quickly search for students using intelligent tags and filters. The final system coalesces these different parts seamlessly, increasing student-company relationships (the primary aim of the system). Our solution enhances everyone's user experience by speeding up the process and offering a slick, well designed interface, which turns what was simply a basic directory service into a fully fledged matchmaking and communications platform.
