\subsection{Challenges}
  \subsubsection{Filtered emails}
    Although not technical, one big challenge we faced was how to reduce the number of irrelevant emails a student was receiving. Two solutions that were not optimal were discussed:
    \begin{itemize}
      \item \textbf{Opt in emails:} students could opt in for receiving certain email catagories based on tags. We soon realised that this would require a lot of maintence by students to continiously update their whitelist with tags as they were being created.
      Not only would it be a lot of work for a student, but students might miss out on exciting emails which do not fall into specific catagories, or a catagory a student had remembered to whitelist. For example the Raspberry Pie is unlikely to fall into a tag group but it's own. If a student forgets to add this to their list they'll miss out entirely on the emails when the likilihood is that they may have been interested.
      \item \textbf{Opt out emails:} students can blacklist tags that they never want to hear from. If an email contains a tag that a student has blacklisted then the student will never get sent this email. Whilst this is a lot closer to our ideal solution we still have the case of a student being interested in C++ say, but blacklisting Java. If an email contains two sections about these two languages and is labelled as containing both the student will never receive the email since Java was in their blacklist.
    \end{itemize}

    We have therefore devised a hybrid solution:
    \begin{itemize}
      \item A student will \textbf{receive} an email if none of the email tags fall in a students blacklist.
      \item A student will \textbf{receive} an email if one or more email tags fall in their blacklist but a tag in the emails list exists in their skill set.
      \item A student will \textbf{not receive} emails from a company they have blocked unless they have signed up to an event in which case they will \textbf{receive} the event related emails only.
      \item A student will \textbf{not receive} an email if any of the tags exist in the emails tags and none exist in the students skill set.
    \end{itemize}

    Furthermore in the student account settings we allow them to choose between receiving this smart email system, all emails, or only personal and event emails.