\subsection{Motivation}
  There is a clear motivation for this project since the system is very out dated and is barely known about by any of the students in the department.
  
  At current it does not freely allow a student to express their interests and skills and as such companies have no way of refining the list of students by these before becoming forced to look at a student's individual CV. This means that companies must go through every student listed in the database whilst searching for one with a particular skill set. For example a web development company may only wish to recruit summer interns who have experience with Ruby on Rails and CoffeeScript. On the current system they must download every single students CV in turn to ascertain if a student would be well suited to the role. This is a time consuming and frustrating process which realistically they will never make it to the bottom of the list. This can severly disadvantage students whose CV's appear at the bottom of the list and unfortunately students have no way of bettering their chances of being found.
  We also believe that it might actually put Corporate Parnters off from using the system to recruit students, instead taking the option to wait for students to come to them.

  The current system has many other flaws, for example once it's been set up there is no way for administrators to tell which Corporate Partners are using the system and how many students are being contacted. What goes on with the system is currently a black hole to the Department of Computing's CPP administrators and they wish to address this. 

  Furthermore the current system does not deal with events and placements at all. When companies wish to advertise an event or placement they have to fill in several forms and return these to the administrators which is then translated into an email that is sent to all students; a mundane and time consuming task. These emails will almost certainly be irrelevant to some students (for example if an event is for females only it will still be sent to the entire department) and thus is often a source of much complaint. 
  Both of these issues could be avoided if the CPP dealt with the creation and advertisment of events and placements.

  Finally other departments have expressed an interest in this system, but it is not deemed up to date enough to pass on to another department which has kick started the immedinate need for CPP 2.0: Connected.
