%TODO: THIS IS A BIT TOO FOCUSED ON EMAILS, PERHAPS ADD SOME MORE COMMENTS.
\subsection{Vast Improvement}
\subsubsection{For Students}
We feel that CPP: Connect gives students a far more personal feel to looking for a job and advertising their abilities than the current system. It also gives them a fairer chance of being found by a company.

As students ourselves, we know that we often don't read the emails that are currently sent via the Corporate Partnership Programme for reasons such as:
\begin{itemize}
  \item We receive far too many emails from CPP, some of which are irrelevant which puts us off.
  \item CPP emails can get lost amidst the other emails we receive from the college.
  \item The emails do not stand out in our inbox and can sometimes be glanced over.
  \item Often when we receive an email we are busy at the time and do not fully register that it might be something of importance.
\end{itemize} 

We have combated most of these problems by the addition of events and placements being advertised on the site itself, which means students will rarely receive emails about them individually. Instead when they log on they can browse through the entire list in their own time, rather than when they may be very busy and not in the right frame of mind to register the opportunity.

Furthermore, for the emails that are sent out, students are allowed to express topics which they don't wish to hear about and these emails will not be sent to them, such as female only information. This helps to make the Corporate Partnership Program a more personal experience and ensure that content remains relevant.

Finally we feel that CPP: Connect provides students a two-way link with companies, giving students the ability to browse companies, and giving them useful contacts to give them the upper hand in applying for internships, placements and graduate jobs.

\subsubsection{For Companies}
We feel that CPP: Connect will provide a richer interface for companies, encouraging them to increase their level of interaction with students. It gives companies a mechanism to advertise themselves to students more extensively with their profile, events and placements.

CPP: Connect gives companies useful tools to find students with the skills they are looking for, without having to trawl through long lists of CVs. We have also given companies intuitive controls to easily carry out actions that they would normally do manually, such as contacting a student directly from their CV and viewing the students that attended an event.

\subsubsection{For CPP Administrators}
We believe our system will ease the lives of the current CPP administrators since they no longer have to forward on emails or translate paper slips into the relevant emails. They can rely on CPP: Connect to do this for them, allowing them to just approve and monitor the process.

We also feel that our system will make it easy for industrial liason co-ordinators of other departments to get started with a Corporate Partnership Programme if they so wished.
